SciPy - some descriptive title here

### 2018-03-31 scipy-1.0/scipy-optimize.tex

\subsubsection{Linear Optimization}

@@

\subsubsection{Multivariable, Nonlinear, Local Optimization}

\subsubsection{Other Improvements}

\paragraph{Nonlinear Root Finding}
Mention df-sane?

\paragraph{Linear Sum Assignment}
(Should this be included?)

\paragraph{Curve Fitting}
As covariant errors are commonplace in scientific data used to fit parametric models, the \texttt{curve\_fit} routine in SciPy 1.0 now accepts a covariance matrix of errors in the data to be fitted.

\paragraph{Global Optimization}

>>>>

\subsubsection*{Linear Optimization}

@@

\subsubsection*{Nonlinear Optimization}

The \texttt{minimize} function provides methods for solving general nonlinear optimization
problems. It unifies several methods with a common interface in order to facilitate
interchanging between solvers with different characteristics.  Table~\ref{tab:minimize} summarizes
all the methods available for solving minimization problems of the type:
\begin{equation}
  \label{eq:minimization-prob}
  \min_x f(x)
\end{equation}
where $f$ is a multivariate function $f: \mathbb{R}^n \rightarrow \mathbb{R}$ and $x \in \mathbb{R}^n$.
\texttt{COBYLA} and \texttt{SLSQP} methods allow nonlinear constraints to be included in the optimization
problems, \texttt{L-BFGS-B} and \texttt{TNC} allow box constraints $x^l \le x \le x^u$,
and the remaining methods are unconstrained optimization methods.

\begin{table}[]
  \centering
  \caption{Optimization methods from \texttt{minimize}.  The field \textit{version added} gives when the algorithm
    was included in SciPy. Algorithm with \textit{version added} equals to 0.6* were added in version 0.6 or before.
    The field \textit{wrapper} indicates whether the implementation available in SciPy wraps a function written in a compiled language
    (e.g. C or FORTRAN). The fields \textit{\nth{1}} and \textit{\nth{2} derivatives}
    indicates whether the first or second order derivatives are required. When \textit{\nth{2} derivatives} is flagged
    with $\sim$ the algorithm does not requires the second-order derivatives from
    the user, it computes an approximation internally and uses it to accelerate the method convergence.
    \textit{Iterative Hessian factorization} indicates algorithms that factorize the Hessian in an iterative way,
    which does not require the explicit matrix factorization or storage of the Hessian.
    \textit{Local convergence} gives a lower bound on the rate of convergence of the iterations sequence once the
    iterate is sufficiently close to the solution. The convergence rates mentioned at the table
    are: linear (L), superlinear (S) and quadratic (Q). When the convergence rate is denoted by S$^*$ the algorithm
    has a superlinear rate for the parameters used in SciPy, but could  achieve a quadratic convergence rate for other parameter choices.
    The \textit{global convergence} is marked for the algorithms with guarantees of convergence to a stationary
    point (i.e. a point $x^*$ for which $\nabla f(x^*) = 0$). The table also indicates which algorithms
    can deal with constraints on the variables. We distinguish between: \textit{bound constraints} (i.e. $x^l \le x \le x^u$),
    \textit{equality constraints} (i.e. $c_{\text{eq}}(x) = 0$) and \textit{inequality constraints} (i.e. $c_{\text{ineq}}(x) \ge 0$).}
  \begin{tabular}{cccccccccccccc}
      & \rotatebox{80}{\texttt{Nelder-Mead}} & \rotatebox{80}{\texttt{Powell}} & \rotatebox{80}{\texttt{COBYLA}} & \rotatebox{80}{\texttt{CG}} & \rotatebox{80}{\texttt{BFGS}}&  \rotatebox{80}{\texttt{L-BFGS-B}} & \rotatebox{80}{\texttt{SLSQP}} & \rotatebox{80}{\texttt{TNC}} & \rotatebox{80}{\texttt{Newton-CG}} & \rotatebox{80}{\texttt{dogleg}} & \rotatebox{80}{\texttt{trust-ncg}} & \rotatebox{80}{\texttt{trust-exact}} & \rotatebox{80}{\texttt{trust-krylov}} \\
    \hline
    Version added &  0.6* &  0.6* &  0.6* &  0.6* &  0.6* &  0.6* &  0.9 &  0.6* &  0.6* & 0.13 & 0.13 & 0.19 & 1.0 \\
    \hline
    Wrapper & & & \cmark & & & \cmark & \cmark & \cmark & &  & & & \cmark \\
    \hline
    \nth{1} derivatives &  & & & \cmark  & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
    \hline
    \nth{2} derivatives &  &  &  &  & $\sim$ & $\sim$ & $\sim$ & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
    \hline
    \makecell{Iterative Hessian \\
    factorization} & & & &  & & & & \cmark & \cmark &  & \cmark &  & \cmark \\
    \hline
    Local convergence& & & & L & S &  L & S & S$^*$ & S$^*$ & Q & S$^*$ & Q & S$^*$  \\
    \hline
    Global convergence & & &  &   & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark  \\
    \hline
    \makecell{Line-search (LS) or\\ trust-region (TR)} & Neither  & LS &  TR & LS & LS & LS & LS & LS & LS & TR & TR & TR & TR \\
    \hline
    Bound constraints &&&\cmark&&&&\cmark&\cmark&\cmark&&&& \\
    \hline
    Equality constraints &&&&&&&\cmark&&&&& \\
    \hline
    Inequality constraint &&&\cmark&&&&\cmark&&&&& \\
    \hline
    References & \cite{nelder_simplex_1965, wright_direct_1996} & \cite{powell_efficient_1964} &
      \cite{powell_direct_1994, powell_direct_1998, powell_view_2007} &
      \cite{polak_note_1969, nocedal_numerical_2006} & \cite{nocedal_numerical_2006} & \cite{byrd_limited_1995, zhu_algorithm_1997} &
      \cite{schittkowski_nonlinear_1982, schittkowski_nonlinear_1982-1, schittkowski_convergence_1983, kraft_software_1988} &
      \cite{nash_newton-type_1984} & \cite{nocedal_numerical_2006}  & 
      \cite{powell_new_1970, nocedal_numerical_2006} &  \cite{steihaug_conjugate_1983, nocedal_numerical_2006} &
      \cite{conn_trust_2000, more_computing_1983} & \cite{gould_solving_1999, lenders_trlib:_2016} \\
    \hline
  \end{tabular}
  \label{tab:minimize}
\end{table}

The available methods implement a variety of strategies for solving optimization problems.
Derivative-free methods (e.g. \texttt{Nelder-Mead}, \texttt{Powell} and \texttt{COBYLA}) are appropriate for minimizing non-differentiable or
noisy objective functions. When the derivatives are available, however, other methods offer faster convergence rates
and have the convergence to a local solution proved.

Available derivative-based methods start with an initial guess and refine it iteratively, seeking
a local solution to the optimization problem. There are algorithms implementing two competing strategies:
line-search and trust-region. The so-called line-search (LS) methods at each iteration choose a direction
and find, approximately, the optimal point in the given direction. Trust-region (TR) methods, on the other
hand, choose a region for which the local approximation is valid and find, approximately, the  best point
inside this \textit{trust-region}.

An example of trust-region method introduced in the latest releases is \texttt{trust-exact},
which a  provides a fast convergence rate by solving  almost exactly the trust-region subproblem.
Its downside is it requires the Hessian to be stored and factored every iteration, which may preclude
the solution of very large problems.

Some of the available optimization methods are appropriate for large-scale problems
(e.g.~problems with more than 1000 variables).
\texttt{CG} does not use second derivatives and is adequate for large-scale problems due to the low storage requirements.
\texttt{L-BFGS-B} maintain a simple and compact representation of the Hessian and is also adequate for large-scale problems.
Finally, \texttt{Newton-CG}, \texttt{trust-ncg} and \texttt{trust-krylov} use the second order derivatives to achieve faster
convergence but are still appropriate for large problems because they factorize the Hessian in an inexact and iterative way,
which does not require the Hessian to be stored.

The method \texttt{trust-krylov}, introduced in the latest release, is as a good compromise between
\texttt{trust-ncg} and \texttt{trust-exact}: it provides a more accurate solution to the trust-region
subproblem than \texttt{trust-ncg} but does not require the Hessian to be stored and factored as in \texttt{trust-exact}.
